Estimating the association between Facebook adoption and well-being

### 2022-09-16 ms.Rmd
Commit synthetic and population data

output: 
  rticles::pnas_article:
    keep_tex: false
---

@@

```{r data-prepare}
# Load and merge data
# Facebook -- this data only exists on FORT
d_fb <- read_csv("data/fb.csv")
# If you are not conducting these analyses on FORT, the above data is not 
# available. Uncomment below to use a synthetic dataset instead.
# d_fb <- read_csv("data/fb-SYNTHETIC.csv")  # If real FB data not available

# Gallup
d_gwp <- read_rds("data/gwp.rds") 
# d_gwp <- read_rds("data/gwp-SYNTHETIC.rds") # If real Gallup data not available

>>>>

output: rticles::pnas_article
---

@@

```{r data-prepare}
# Load and merge data
# Facebook -- this data only exists on FORT
d_fb <- read_csv("data-raw/fb.csv")
# If you are not conducting these analyses on FORT, the above data is not 
# available. Uncomment below to use a synthetic dataset instead.
# d_fb <- read_csv("data/fb-SYNTHETIC.csv")  # If real FB data not available

# Gallup
d_gwp <- read_rds("data-raw/gwp.rds") 
# d_gwp <- read_rds("data/gwp-SYNTHETIC.rds") # If real Gallup data not available
